Control of Prosumer Networks

### 2016-03-17 Article.tex
new figure style

\begin{figure}
	\label{fig:submodular}
	\begin{center}
	\includegraphics[scale=.3]{./figure_1/figure_1}
	\caption{Submodularity example with sensor placements.}
	\end{center}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=.38]{./figure_2/figure_2.pdf}
\caption{At time $ t_k=4500 $, $P_i(t_k) = P_i(t_{k-1}) + \delta P$ for some random node i (perturbation). Consequently, the frequencies $ \dot{ \theta }_i $ deviate from the synchronized state. At time $ t_k + d = 5000$, optimal control inputs (see equation \ref{eq:ustar}) are injected such that the system is brought to the synchronized state at time $ t_k + d + T = 5500 $ (T is the control time).}

@@

\begin{figure}
\includegraphics[scale=.35]{./figure_3/figure_3}
\caption{Logarithm of average control energy $log(\mathcal{E})$ against size of control set $n_D$ for random and optimized driver sets. Topologies are drawn from a Barabasi-Albert model with $ N_{nodes} = 50 $, power and line capacity distributions are random. $10^4$ instances are considered and the results are displayed as dots. The lines shows the average for both case. }
\label{fig:densities}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=.25]{./figure_4/figure_4}
\caption{ $ n_D $ against link probability p for erdos-renyi topologies ($ N=100 $). Curves are averaged over 100 realizations. The top three curves show the results for the three metrics taken into consideration when all constraints are considered (see Level 2 in the main text). The bottom three curves exhibit the results for the same metrics when only the full controllability constraint is considered (see Level 1).}
\label{fig:erdos_renyi}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=.25]{./figure_5/figure_5}
\caption{$n_D$ against $N_{clusters} $ for different values of $ p_{in} $ and $ p_{out} = 0.1 $. $ N=200 $ and curves are averaged over 100 realizations.}
\label{fig:block_model_1}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=.25]{./figure_6/figure_6}
\caption{$n_D$ against $ p_{in} $ for systems of $N=200 $, $p_{out} = 0.1 $, and for different values of $N_{clusters} $. The curves are averaged over 100 realizations.}
\label{fig:block_model_2}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=.37]{./figure_7/figure_7}
\caption{$n_D$ against the relative standard deviation of the capacity distribution of the batteries $ \frac{ \sigma_{ \lambda } }{ \mu_{ \lambda} } $. The dots are averages over 100 realizations and the curves are obtained using a Savitzky-Golay filter, each color shows the results for a given metric. The graphs are erdos-renyi with $N=100$ and $p=0.3$, and $\mu_{\lambda} = 100 $ units. }
\label{fig:batteries_variance}
\end{figure}

>>>>

\begin{figure}
	\label{fig:submodular}
	\begin{center}
	\includegraphics[scale=.25]{./figure_1/figure_1}
	\caption{Submodularity example with sensor placements.}
	\end{center}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=.55]{plot5.pdf}%./figure_2/figure_2.pdf}
\caption{At time $ t_k=4500 $, $P_i(t_k) = P_i(t_{k-1}) + \delta P$ for some random node i (perturbation). Consequently, the frequencies $ \dot{ \theta }_i $ deviate from the synchronized state. At time $ t_k + d = 5000$, optimal control inputs (see equation \ref{eq:ustar}) are injected such that the system is brought to the synchronized state at time $ t_k + d + T = 5500 $ (T is the control time).}

@@

\begin{figure}
\includegraphics[scale=.55]{plot4.pdf}%./figure_3/figure_3}
\caption{Logarithm of average control energy $log(\mathcal{E})$ against size of control set $n_D$ for random and optimized driver sets. Topologies are drawn from a Barabasi-Albert model with $ N_{nodes} = 50 $, power and line capacity distributions are random. $10^4$ instances are considered and the results are displayed as dots. The lines shows the average for both case. }
\label{fig:densities}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=.55]{plot3.pdf}%./figure_4/figure_4}
\caption{ $ n_D $ against link probability p for erdos-renyi topologies ($ N=100 $). Curves are averaged over 100 realizations. The top three curves show the results for the three metrics taken into consideration when all constraints are considered (see Level 2 in the main text). The bottom three curves exhibit the results for the same metrics when only the full controllability constraint is considered (see Level 1).}
\label{fig:erdos_renyi}
\end{figure}

@@

\begin{figure*}
	\begin{center}
		\includegraphics[scale=.5]{Blockmodel.png}
		\caption{left panel : $n_D$ against $N_{clusters} $ for different values of $ p_{in} $ and $ p_{out} = 0.1 $. $ N=200 $ and curves are averaged over 100 realizations. right panel : $n_D$ against $ p_{in} $ for systems of $N=200 $, $p_{out} = 0.1 $, and for different values of $N_{clusters} $. The curves are averaged over 100 realizations.}
	\end{center}
\end{figure*}

%\begin{figure}
%\includegraphics[scale=.25]{./figure_5/figure_5}
%\caption{$n_D$ against $N_{clusters} $ for different values of $ p_{in} $ and $ p_{out} = 0.1 $. $ N=200 $ and curves are averaged over 100 realizations.}
%\label{fig:block_model_1}
%\end{figure}

@@

%\begin{figure}
%\includegraphics[scale=.25]{./figure_6/figure_6}
%\caption{$n_D$ against $ p_{in} $ for systems of $N=200 $, $p_{out} = 0.1 $, and for different values of $N_{clusters} $. The curves are averaged over 100 realizations.}
%\label{fig:block_model_2}
%\end{figure}

@@

\begin{figure}
\includegraphics[scale=.55]{plot2.pdf}%./figure_7/figure_7}
\caption{$n_D$ against the relative standard deviation of the capacity distribution of the batteries $ \frac{ \sigma_{ \lambda } }{ \mu_{ \lambda} } $. The dots are averages over 100 realizations and the curves are obtained using a Savitzky-Golay filter, each color shows the results for a given metric. The graphs are erdos-renyi with $N=100$ and $p=0.3$, and $\mu_{\lambda} = 100 $ units. }
\label{fig:batteries_variance}
\end{figure}
